A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-09-15 paper/main.tex
clean methods until data legend

\subsection*{Stimulus}
% stimulus != DVD but ``research cut''
We annotated speech in the slightly shortened ``research cut'' of the movie
\citep{hanke2016simultaneous} and its temporally aligned audio-description
\citep{hanke2014audiomovie}.
% movie source
For the movie stimulus, we used the audio track of the German DVD release
\citep{ForrestGumpDVD}.
% audio source
For the audio-only stimulus, we used the movie's audio-description that was
broadcast as an additional audio track for visually impaired listeners on Swiss
public television \citep{ForrestGumpGermanAD}.
% diff in audio AV vs. AO
The plot of the movie is already carried by an off-screen voice of the main
character Forrest Gump. In the largely identical audio-description, a male
narrator additionally describes essential aspects of the visual scenery when
there is no off-screen voice, dialog, or other relevant auditory content.

\subsection*{Annotation procedure}
% preliminary annotations
Preliminary, manual orthographic transcriptions of dialogues, non-speech
vocalizations (e.g. laughter or groaning) and the script for the
audio-description's narrator were merged and converted to Praat's
\citep{boersma2019praat} TextGrid format.
% preparing annotation in Praat before forced alignment
% \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
The merged transcription containing a rough onset and offset for usually a
couple of sentences was edited in Praat for manual validation against the
actual content of the audio material.
% steps conducted
The following steps were done in several passes to iteratively improve the
quality of the data: approximate temporal onsets and offsets were corrected, and
intervals containing several sentences were split into intervals containing only
one sentence.
% dropping of sentences hard to understand
When two or more persons were speaking simultaneously the less dominant voice
was dropped. Low volume background speech (especially occurring during music or
continuous environmental noise) or low volume non-speech vocalizations which
were subjectively assessed to be incomprehensible for the audience were dropped,
too.

% intro for forced aligner
We then used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
algorithmically identify the exact onset of offset of each sentence, and the
onset and offset of each word and phoneme.
% preparing other inputs before forced alignment pronunciation dictionary
% http://prosodylab.org
% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
To enable the aligner to look up the phonemes embedded within each word, we
chose a German pronunciation dictionary provided by Prosodylab \citep
{gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the
pronunciation of phonemes.
% extending the dictionary with formerly unknown German words
To improve the detection rate of the automatic alignment, the dictionary was
manually updated with German words that occur in the stimuli but were originally
missing in the dictionary.
% \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
% English words in the otherwise German stimulus
The pronunciation of English words and phonemes occurring in the otherwise
German audio track was taken from an English pronunciation dictionary (following
the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab
(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).
% performing the forced alignment audio input to the aligner
The audio track was converted from FLAC to WAV via FFmpeg \citep{ffmpeg} to meet
the aligner's requirements.
% inputs
This WAV file, the merged transcription, and the updated dictionary were
submitted to the aligner that first trained an acoustic model on the data and
then performed the alignment.

>>>>

\subsection*{Stimulus}
% stimulus != DVD but ``research cut''
We annotated speech in the slightly shortened ``research cut'' \citep{hanke2014audiomovie, hanke2016simultaneous} of the movie and its
temporally aligned audio-description that was broadcast as an additional audio
track for visually impaired listeners on Swiss public television
\citep{ForrestGumpGermanAD}.
%  what the AO contains
The plot of the movie is already carried by an off-screen voice of the main
character Forrest Gump. In the largely identical audio-description, a male
narrator additionally describes essential aspects of the visual scenery when
there is no off-screen voice, dialog, or other relevant auditory content.

\subsection*{Annotation procedure}
% preliminary annotations
Preliminary, manual orthographic transcriptions of dialogues, non-speech
vocalizations (e.g. laughter or groaning) and the script for the
audio-description's narrator were merged and converted to Praat's
\citep{boersma2019praat} TextGrid format.
% preparing annotation in Praat before forced alignment
% \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
This merged transcription that contained a rough onset and offset for usually a
couple of sentences was edited in Praat for manual validation against the actual
content of the audio material.
% steps conducted
The following steps were done in several passes to iteratively improve the
quality of the data: approximate temporal onsets and offsets were corrected, and
intervals containing several sentences were split into intervals containing only
one sentence.
% dropping of sentences hard to understand
When two or more persons were speaking simultaneously the less dominant voice
was dropped. Low volume non-speech vocalizations or low volume background speech
(especially during music or continuous environmental noise) which were
subjectively assessed to be incomprehensible for the audience were dropped, too.

% intro for forced aligner
We then used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
algorithmically identify the exact onset of offset of each sentence, and the
onset and offset of each word and phoneme.
% preparing other inputs before forced alignment pronunciation dictionary
% http://prosodylab.org
% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
To enable the aligner to look up the phonemes embedded within each word, we
chose a German pronunciation dictionary provided by Prosodylab \citep
{gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the
pronunciation of phonemes.
% extending the dictionary with formerly unknown German words
To improve the detection rate of the automatic alignment, the dictionary was
manually updated with German words that occur in the stimuli but were originally
missing in the dictionary.
% \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
% English words in the otherwise German stimulus
The pronunciation of English words and phonemes occurring in the otherwise
German audio track was taken from an English pronunciation dictionary (following
the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab
(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).
% performing the forced alignment audio input to the aligner
The audio track of the audio-description was converted from FLAC to WAV via
FFmpeg \citep{ffmpeg} to meet the aligner's input requirements.
% inputs
This WAV file, the merged transcription, and the updated dictionary were
submitted to the aligner that first trained an acoustic model on the data and
then performed the alignment.
